Variety in the Implementation of Nonlinear Least Squares Program Codes

### 2022-06-12 VarietyInNLS/VarietyInNonlinearLeastSquaresCodes.Rmd
cleanup of Variety. Removed test problems as too long

We have a versions of the Nashlib Algorithm 23 in BASIC, Fortran, Pascal, Matlab/Octave and R, 
with Python under consideration. There may be dialects of these programming languages,
giving rise to other variations. Features of these computing environments can greatly
ease or hinder the building of well-structured codes. See
*git@github.com:pcolsen/Nash-Compact-Numerical-Methods.git*.

@@

The above uses the intermediate code in function `lm.fit()`. This uses a QR solver, but
it is written as a wrapper in C calling a Fortran routine (in the Fortran 77 dialect).

?? Should we put in the structure and where the code is located?

I believe that the structure of lm() predates the availability of the family
of `qr.xxx()` functions for R. These allow us to access the QR approach 
directly.

@@

>>>>

We have a versions of the Nashlib Algorithm 23 in BASIC, Fortran, Pascal, Matlab/Octave and R, 
with Python under consideration. There may be dialects of these programming languages,
giving rise to other variations. Features of these computing environments can greatly
ease or hinder the building of well-structured codes. See
*git@github.com:pcolsen/Nash-Compact-Numerical-Methods.git*. The principal merit
of having these multiple implementations is that they illustrate the interaction between
algorithm and programming language. Unfortunately, creating them is a lot of effort for
no appreciable new capability. That is, they are an interesting intellectual exercise
that may incidentally afford minor benefits to a few individual users.

@@

The above uses the intermediate code in function `lm.fit()`. This uses a QR solver, but
it is written as an R wrapper calling a C routine, which in turn calls a local Fortran 77
driver for Linpack (@Dongarra79) routines
"dqrdc" and "dqrsl". The R wrapper is part of the R source distribution
(here we refer to R-4.0.0, but I believe that the location of the code has not changed over a
fairly long sequence of releases). It is found in src/library/stats/R/lm.R. This calls
the C routine "Cdqrls" in src/library/stats/src/lm.c. The Fortran (strictly Fortran 77)
code "dqrls.f" is found in src/appl/.

I believe that the structure of lm() predates the availability of the family
of `qr.xxx()` functions for R, which allow us to access the QR approach 
directly.

@@

This rather long-winded pursuit of the convoluted code structure underlines how 
much effort must be expended, and how much expertise over several programming
languages is needed to properly alter or maintain the code for `nls()` and other
functions within R that do so much computation.
